Initial Analysis

### 2019-12-23 Initial_Analysis.Rmd
Updataed results

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "wesanderson",
  "tidyverse", # for all data wrangling and ggplot
  "janitor", # for data cleaning
  "tidytext", # to order the facet wrap https://juliasilge.com/blog/reorder-within/
  # "circlize", # For circular plot
  # "ggimage", #for reading images to the circular plot
  # "ggrepel", # for nice plot labels
  # "ggsflabel", # for nice sf_plots labels
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  # "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "parallel", # for parallelization
  # "taxize", # For getting species names
  "rfishbase", # for species ecosystem affinity
  "zoo" #for runing mean
)

@@

@@

@@

# Requires Clean_sau_eez_fes

CleanResults <- function(Data){

@@

  Clean_Results$Neighbour <- Clean_Results$Neighbour %>% 
    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
    gsub(" R<e9>union (France)","Réunion",.)

  Clean_Results$CT_fishing_entity <- Clean_Results$CT_fishing_entity %>% 
    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
    gsub(" R<e9>union (France)","Réunion",.)

@@

# x <- Clean_Results(Discrete_Data)

@@

@@

Clean_sau_eez_fes <- sau_eez_fes %>% 
  gather("Type","fishing_region",2,4) %>% 
  left_join(sau_eez_fes,
            by = ("fishing_entity_id")
  ) %>% 
  group_by(eez_name,fishing_entity) %>% 
  summarise(n())

# UN Regions dataset
UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
  clean_names() %>% 
  group_by(fishing_entity = country_or_area,
           georegion = region_name,
           sub_region = sub_region_name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
    # fishing_entity = gsub( "United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
    fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
  )

@@

# Load it!
World_land_sf <- st_read(dsn = path_world_land,
                         layer =file_path_sans_ext(fnam_world_land)) %>% 
  rename(fishing_entity = NAME)

@@

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Revenue_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
  ungroup() %>% 
  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",
                                 ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
                                 ),
         Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
         Bins_Plot = cut(Total_USD,breaks = Rev_Breaks,
                         labels = c('super low', 'low','median','high','super high'),
                         dig.lab = 5 # Removes scientific notaion
                         )
  ) %>% 
  filter(Total_USD > 0)

@@

### Revenue Data
Subregion_Data <- Revenue_Country %>% 
  left_join(Catch_Country,
             by = "fishing_entity") %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region) %>% 
  summarise_if(is.numeric,sum,na.rm=T)

@@

label_data_rev <- Subregion_Data_Trans %>% 
  arrange(Total_USD) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )
  )

label_data_catch <- Subregion_Data_Trans %>% 
  arrange(fishing_entity_catch) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )
  )

@@

Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
# Labels_Trans <- c(paste(unique(Transboundary_Spp$Bins)),"NA")
# Labels_Rev <- unique(Revenue_Country$Bins)

Labels_Rev <- c("(1-10]",paste(Bins_Rev[2:5]))

# Make map
Map <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,Total_USD)), colour = "grey80",size = 0.1) +
  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
  # rev(wes_palette(n = 4, name = "Darjeeling2"))
  # ),
  # na.value = "white"
  # ) +
  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                  "#00A08A",#"#00A08A", #green
                                  "#F2AD00",#"#F2AD00", # Yellow
                                  "#F98400",#"#F98400", #Orange
                                  "#FF0000"#,"#FF0000" #Red
  ),
  # na.value = "white"
  na.translate = F
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map() +
  # Transboundary labels
  annotate("text", 
           x =(c(-85.5,-30,25,81,136)+5),
           y = -93.5,
           label = Labels_Trans, 
           color="black", 
           size=3, 
           angle=0, 
           # fontface="bold",
           hjust=0) +
  # Revenue labels
  annotate("text", 
           x =(c(-85.5,-31,20,75,131)+5),
           y = -110,
           label = Labels_Rev, 
           color="black", 
           size=3, 
           angle=0, 
           # fontface="bold",
           hjust=0) +
  # Legend Titles
  annotate("text", 
           x =-180,
           y = -93.5,
           label = "Transboundary Spp. (n)", 
           color="black", 
           size=3, 
           angle=0, 
           fontface="bold",
           hjust=0) +
  annotate("text", 
           x =-180,
           y = -110,
           label = "Revenue (Million USD)", 
           color="black", 
           size=3, 
           angle=0, 
           fontface="bold",
           hjust=0) +
  theme(
    legend.box.margin = margin(t = -54, l = 130),
    legend.text = element_blank()#,
  ) +
  guides(fill = guide_legend(nrow = 1))

# ggsave("Map.png",
#        Map,
#         width = 10,
#          height = 10,
         # units = "in")
# Map

@@

# Revenue Plot
# Set plot limits
max_lim <- max(Subregion_Data_Trans$Total_USD)

@@

Rev_Plot <- ggplot(data = Subregion_Data_Trans, 
                   aes(x=reorder(id,Total_USD),
                       y=Total_USD, 
                       fill=Total_USD
                   )
) +    
  ylim(-1500, max_lim+10)+
  geom_bar(stat="identity") +
  theme_minimal() +
  theme(
    legend.position = c(0.74,0.60),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-10,"cm")
  )  +
  # Base line
  geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
               colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_rev, 
            aes(x=id,
                y=Total_USD+10,
                # label=round(Total_USD_Billion),
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_rev$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       colours = pal) +
  guides(fill = guide_colorbar(label.position = "left")
  )

### Catch plot

max_lim <- max(Subregion_Data_Trans$fishing_entity_catch)

Catch_Plot <- ggplot(data = Subregion_Data_Trans, 
                     aes(x=reorder(id,fishing_entity_catch),
                         y=fishing_entity_catch, 
                         fill=fishing_entity_catch
                     )
) +    
  ylim(-1.5, max_lim+1) +
  geom_bar(stat="identity") +
  theme_minimal() +
  theme(
    legend.position = c(0.1,0.60),
    # legend.position = "right",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-5,"cm")
    # plot.margin = margin(0,0,-5,0,"cm")
  )  +
  # Base line
  geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
               colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_catch, 
            aes(x=id,
                y=fishing_entity_catch+0.1,
                # label=round(Total_USD_Billion),
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_catch$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       colours = pal)

# Catch_Plot

@@

# library(ggpubr)
# library(cowplot)

plot <- ggdraw() +
  # map
  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0.1, y = 0.07, width = 0.5, height = 0.4) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.45, y = 0.07, width = 0.5, height = 0.4) +

  # Labeks
  draw_plot_label(label = c("A", "B"), 
                  size = 20,
                  x = c(0, 0), 
                  y = c(1, 0.45)
  ) +
  draw_plot_label(label = c("Revenue (USD) | Catch (Tones)","(Million)"), 
                  size = 8,
                  x = c(0.333,0.493), 
                  y = c(0.30,0.28)
  )

save_plot(
  # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
  "Plot.png",
  plot,
  base_height = 8,
  base_width = 8
)

@@

PeRu <- c("Peru", "Russian Federation","Russia", "Chile", "United States of America","USA")

Total_PeRu <- Revenue_Country %>% 
  filter(fishing_entity %in% PeRu) %>% 
  select(1:2) %>% 
  mutate(fishing_entity = ifelse(fishing_entity == "Russia","Russian Federation",
                                 ifelse(fishing_entity == "United States of America","USA",fishing_entity))
  )

@@

@@

# Transboundary Species shapefile
World_sf_si <- RFMOs_sf %>%
  rename(Territory = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.0001) %>%
  left_join(Transboundary_Spp, by ="Territory")

@@

# Set a number of 'empty bar' to add at the end of each Georegion
Char <- as.factor(Status_Data_Plot$group) # Set groups to factors

@@

# Transform data in a tidy format (long format)
data <- Status_Data_Plot

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(Status_Data_Plot$observation))
to_add <- data.frame(matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Status_Data_Plot)) )
colnames(to_add) <- colnames(Status_Data_Plot)
to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
to_add$value <- NA
to_add$observation <- NA
# to_add$individual <- to_add$group

>>>>

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "wesanderson",
  "tidyverse", # for all data wrangling and ggplot
  "janitor", # for data cleaning
  "tidytext", # to order the facet wrap https://juliasilge.com/blog/reorder-within/
  "cowplot", # for figures 1 and 3
  # "ggimage", #for reading images to the circular plot
  # "ggrepel", # for nice plot labels
  # "ggsflabel", # for nice sf_plots labels
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  # "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "parallel", # for parallelization
  # "taxize", # For getting species names
  "rfishbase", # for species ecosystem affinity
  "zoo" #for runing mean
)

@@

- Rebuilding (Recovering),	Year of landing > year of post-max. min. landing AND post-max. min. landing < 10% of max. landing AND landing is 10-50% of max. landing
- Developing,	Year of landing < year of max. landing AND landing is < or = 50% of max. landing OR year of max. landing = final year of landing
- Max Exploited,	Landing > 50% of max. landing
- Over exploited,	Year of landing > year of max. landing AND landing is between 10-50% of max. landing
- Collapsed,	Year of landing > year of max. landing AND landing is < 10% of max. landing

@@

# RFMO Analysis

```{r RFMO_Data, eval = F}

RFMO_Data <- read.delim("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/RFMO/RFMO_procedure_outcome.csv")

x <- RFMO_Data %>% 
  mutate(
    x = gsub("<.*?>", "", RFMO_Data$primary_species),
    y = gsub("[\\(\\)]", "", regmatches(x, gregexpr("\\(.*?\\)", x)))
  )

# Save to remove "" and pass to colomuns in excell
# write.csv(x,
#           "rfmos.csv")

rfmos <- read.csv("~/Github/FishForVisa/rfmos.csv")
  View(rfmos)

list <- rfmos$Taxa

clean_rfmos <- rfmos %>% 
  gather("taxa","taxon_name",y:X.21) %>% 
  filter(taxon_name != "") %>% 
  select(RFMO_name = name,
         contracting_parties,
         area,
         taxon_name)

# write_csv(clean_rfmos,
#           "clean_rfmos.csv")

### Join with exploited species

clean_rfmos <- clean_rfmos %>% 
  left_join(Exploited_Species)

@@

# Requires Clean_sau_eez_fes
# Data <- Results_Trans
CleanResults <- function(Data){

@@

  Clean_Results$Neighbour <- Clean_Results$Neighbour %>% 
    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
    gsub("R<e9>union (France)","Réunion",.)

  Clean_Results$CT_fishing_entity <- Clean_Results$CT_fishing_entity %>% 
    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
    gsub("R<e9>union (France)","Réunion",.)

@@

@@

# Set Jurisdiction to EEZ or RFMO
# Jurisdiction <- "EEZ"
Jurisdiction <- "RFMO"

@@

Clean_sau_eez_fes <- sau_eez_fes %>% 
  gather("Type","fishing_region",2,4) %>% 
  left_join(sau_eez_fes,
            by = ("fishing_entity_id")
  ) %>% 
  group_by(eez_name,fishing_entity) %>% 
  summarise(n()) %>% 
  ungroup() %>% 
  ### Manually Fix names for estimating catch
  mutate(eez_name = ifelse(eez_name =="Greece (without Crete)","Greece",
                           ifelse(eez_name =="Greenland (Denmark)","Greenland",
                                  ifelse(eez_name =="United Kingdom (UK)","United Kingdom",
                                         ifelse(fishing_entity =="Italy","Italy",
                                                ifelse(eez_name =="Chile (mainland)","Chile",
                                                       ifelse(fishing_entity =="Brazil","Brazil",
                                                              ifelse(eez_name == "Ecuador (mainland)", "Ecuador",
                                                                     ifelse(eez_name =="Portugal (mainland)","Portugal",
                                                                            ifelse(fishing_entity == "Korea (North)","Korea (North)",
                                                                                   paste(eez_name))
                                                                            )
                                                                     )
                                                              )))))),
         fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
         )
  )

# UN Regions dataset
UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
  clean_names() %>% 
  group_by(fishing_entity = country_or_area,
           georegion = region_name,
           sub_region = sub_region_name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
    fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
    # fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
    fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),,
    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
  )

@@

# Load it!
World_land_sf <- st_read(dsn = path_world_land,
                         layer =file_path_sans_ext(fnam_world_land)) %>% 
  rename(fishing_entity = NAME) %>% 
  mutate(
    fishing_entity = gsub("Russia", "Russian Federation",fishing_entity),
    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Dem. Rep. Congo", "Congo, R. of",fishing_entity),
    fishing_entity = ifelse(fishing_entity=="Congo", "Congo (ex-Zaire)",paste(fishing_entity))
         )

# View(unique(World_land_sf$fishing_entity))

@@

# View(unique(World_sf$eez_name))

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Revenue_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
  ungroup() %>% 
  mutate(#fishing_entity = ifelse(fishing_entity == "USA","United States of America",
                                 # ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
                                 # ),
         Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
         Bins_Plot = cut(Total_USD,breaks = Rev_Breaks,
                         labels = c('super low', 'low','median','high','super high'),
                         dig.lab = 5 # Removes scientific notaion
                         )
  ) %>% 
  filter(Total_USD > 0)

@@

### Revenue Data
Subregion_Data <- Revenue_Country %>% 
  left_join(Catch_Country,
             by = "fishing_entity") %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region) %>% 
  summarise_if(is.numeric,c(sum = sum,
                            m = mean,
                            sd = sd),
               na.rm=T)

@@

label_data_rev <- Subregion_Data_Trans %>% 
  arrange(Total_USD_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )
  )

label_data_catch <- Subregion_Data_Trans %>% 
  arrange(fishing_entity_catch_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )
  )

@@

Labels_Trans <- c("(1-29]",paste(Bins_Trans[2:5]))
Labels_Rev <- c("(1-10]",paste(Bins_Rev[2:5]))

# Make map
Map <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,Total_USD)), colour = "grey80",size = 0.1) +
  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                  "#00A08A",#"#00A08A", #green
                                  "#F2AD00",#"#F2AD00", # Yellow
                                  "#F98400",#"#F98400", #Orange
                                  "#FF0000"#,"#FF0000" #Red
  ),
  na.translate = F
  ) +
  ggtheme_map() +
  # Transboundary labels
  annotate("text", 
           x =(c(-85.5,-30,25,81,136)+5),
           y = -93.5,
           label = Labels_Trans, 
           color="black", 
           size=3, 
           angle=0, 
           # fontface="bold",
           hjust=0) +
  # Revenue labels
  annotate("text", 
           x =(c(-85.5,-31,20,75,131)+5),
           y = -110,
           label = Labels_Rev, 
           color="black", 
           size=3, 
           angle=0, 
           # fontface="bold",
           hjust=0) +
  # Legend Titles
  annotate("text", 
           x =-180,
           y = -93.5,
           label = "Transboundary Spp. (n)", 
           color="black", 
           size=3, 
           angle=0, 
           fontface="bold",
           hjust=0) +
  annotate("text", 
           x =-180,
           y = -110,
           label = "Revenue (Million USD)", 
           color="black", 
           size=3, 
           angle=0, 
           fontface="bold",
           hjust=0) +
  theme(
    legend.box.margin = margin(t = -54, l = 130),
    legend.text = element_blank(),
  ) +
  guides(fill = guide_legend(nrow = 1))

@@

# Revenue Plot

@@

# Set plot limits
max_lim <- max(Subregion_Data_Trans$Total_USD_sum) +10

Rev_Plot <- ggplot(
  # Regional plots
  data = Subregion_Data_Trans, 
  aes(
    x=reorder(id,Total_USD_sum),
    y=Total_USD_sum, 
    fill=Total_USD_sum
  )
) +    
  ylim(-1500, max_lim) +
  geom_bar(stat="identity") +
  # Regional averages
  geom_point(data = Subregion_Data_Trans,
             aes(
               x=reorder(id,Total_USD_sum),
               y=Total_USD_m
             ),
             colour = "black",
             alpha = 0.5
  ) +
  # Regional sds
  geom_errorbar(
    aes(
      ymin=ifelse(Total_USD_m-Total_USD_sd <= 0,0,Total_USD_m-Total_USD_sd), # sets lower to 0
      ymax=Total_USD_m+Total_USD_sd
    ), 
    width=.2,
    position=position_dodge(.9),
    alpha = 0.5) +
  # Looking good
  theme_minimal() +
  theme(
    legend.position = c(0.73,0.60),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-10,"cm")
  )  +
  # Base line
  # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
  #              colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_rev, 
            aes(x=id,
                y=Total_USD_sum+10,
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_rev$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       colours = pal,
                       limits = c(0,16500),
                       breaks = seq(0,16000,4000)) +
  guides(fill = guide_colorbar(label.position = "left")
  )

###____________###
### Catch plot
###____________###
max_lim <- max(Subregion_Data_Trans$fishing_entity_catch_sum) +1

Catch_Plot <- ggplot(data = Subregion_Data_Trans, 
                     aes(x=reorder(id,fishing_entity_catch_sum),
                         y=fishing_entity_catch_sum, 
                         fill=fishing_entity_catch_sum
                     )
) +    
  ylim(-2.1, max_lim) +
  geom_bar(stat="identity") +
  # Regional averages
  geom_point(data = Subregion_Data_Trans,
             aes(
               x=reorder(id,fishing_entity_catch_sum),
               y=fishing_entity_catch_m
             ),
             colour = "black",
             alpha = 0.5
  ) +
  # Regional sd's
  geom_errorbar(
    aes(
      ymin=ifelse(fishing_entity_catch_m-fishing_entity_catch_sd <= 0,0,fishing_entity_catch_m-fishing_entity_catch_sd),
      ymax=fishing_entity_catch_m+fishing_entity_catch_sd
    ), 
    width=.2,
    position=position_dodge(.9),
    alpha = 0.5) +
  theme_minimal() +
  theme(
    legend.position = c(0.1,0.60),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-5,"cm")
  )  +
  # Base line
  # geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
  #              colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_catch, 
            aes(x=id,
                y=fishing_entity_catch_sum+0.1,
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_catch$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       limits = c(0,16.5),
                       breaks = seq(0,16,4),
                       colours = pal

@@

plot <- ggdraw() +
  # map
  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
  # Labeks
  draw_plot_label(label = c("A", "B"), 
                  size = 20,
                  x = c(0, 0), 
                  y = c(1, 0.45)
  ) +
  draw_plot_label(label = c("Revenue (USD) | Catch (Tones)","(Million)"), 
                  size = 8,
                  x = c(0.330,0.485), 
                  y = c(0.31,0.29)
  )

save_plot(
  paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
  # "Plot.png",
  plot,
  base_height = 8,
  base_width = 8
)

@@

PeRu <- c("Peru", "Russian Federation", "Chile", "USA")

Total_PeRu <- Revenue_Country %>% 
  filter(fishing_entity %in% PeRu) %>% 
  select(1:2)

@@

### Statistical differences

We used a one-way ANOVA to determine significant differences within regions for transboundary fisheries catches and revenue with a Tukey's HSD post-hoc test.

```{r statistics_fig1, eval = F, echo = T}

### Using ANOVA to estimate significan differences within regions for revenue and catch of transboundary species

### Prepare Data
Subregion_Data_stats <- Revenue_Country %>% 
  left_join(Catch_Country,
             by = "fishing_entity") %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  select(fishing_entity,sub_region,Total_USD,fishing_entity_catch)

# Revenue ANOVA
Rev_aov <- aov(Total_USD~sub_region, data = Subregion_Data_stats)
Rev_aov
summary(Rev_aov)

# Df    Sum Sq Mean Sq F value  Pr(>F)    
# sub_region   16  75628526 4726783    4.91 4.2e-08 ***
# Residuals   157 151140183  962676

#### There are significant differences. But between what?

#  Post-hoc analysis
TukeyHSD(Rev_aov)

# Northern America sig than everyone except for Eastern Asia
# Eastern Asia sig with everyone except with Eastern Europe and North Am.

### Catch ANOVA

Catch_aov <- aov(fishing_entity_catch~sub_region, data = Subregion_Data_stats)
Catch_aov

summary(Catch_aov)

# sub_region   16  50.63   3.164   3.767 7.2e-06 ***
# Residuals   155 130.22   0.840                    
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

#  Post-hoc analysis
TukeyHSD(Catch_aov)
```

@@

head(RFMOs_sf)

# Transboundary Species shapefile
World_sf_si <- RFMOs_sf %>%
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_simplify(preserveTopology = TRUE, dTolerance = 0.0001) %>%
  left_join(Transboundary_Spp, by ="eez_name")

ICC <- World_sf_si %>% 
  filter(eez_name == "ICCAT")

@@

# Set a number of 'empty bar' to add at the end of each Georegion
Char <- as.factor(Status_Plot_Data$group) # Set groups to factors

@@

# Transform data in a tidy format (long format)
# data <- Status_Data_Plot

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(Status_Plot_Data$observation))
to_add <- data.frame(matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Status_Plot_Data)) )
colnames(to_add) <- colnames(Status_Plot_Data)
to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
Status_Plot_Data <- rbind(Status_Plot_Data, to_add) # Problem converts to list
# Status_data <- bind_rows(data,to_add)
Status_Plot_Data <- Status_Plot_Data %>% arrange(group, individual)
Status_Plot_Data$id <- rep( seq(1, nrow(Status_Plot_Data)/nObsType) , each=nObsType)

# to_add$value <- NA
# to_add$observation <- NA
# to_add$individual <- to_add$group
